---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# INCLUDE Shiny Template

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Welcome to INCLUDE. This repository will serve as a guide for developing
shiny applications and contains the most basic golem shiny application
structure.  Here were the steps that went into creating this repository.

1. Create Golem Shiny App: `golem::create_golem()` as documented [here](https://engineering-shiny.org/setting-up-for-success.html#create-a-golem)
1. Utilize [renv](https://engineering-shiny.org/build-yourself-safety-net.html#renv) to set up your R environment
1. Update readme by modifying README.Rmd (not README.md):

  ```
  devtools::build_readme()
  ```

1. Add golem modules. More information [here](https://engineering-shiny.org/build-app-golem.html#submodules-and-utility-functions)

  ```
  golem::add_module( name = "hello_world" )
  ```

1. Add tests. More information [here](https://engineering-shiny.org/build-app-golem.html#add-tests)

  ```
  usethis::use_test( "app" )
  ```


## Installation

You can install the released version of includeshinytemplate from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("includeshinytemplate")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("include-dcc/include-shiny-template")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(includeshinytemplate)
## basic example code
```

